Individual and Differential Harm in Redistricting

### 2022-05-16 paper/paper.Rmd
AL priors

This intuition is confirmed by a closer analysis, summarized in Figure \ref{fig:al-maps}(f).
Across the state, the average harm is 0.075, which translates to around 151,000 voters.
Of these harmed voters, around 128,000 are Black, while 23,000 are White.
Similarly, 140,000 are Democratic, while only 11,000 are Republican.
Of course, the total number of each of these groups of voters is very different.
Normalizing by group sizes, the expected harm for a Black Democrat is 0.23, for a Black Republican is 0.026, for a White Democrat is 0.084, and for a White Republican is 0.0082.
Thus while the challenged plan differentially harms both Black voters and Democratic voters, it *especially* harms Black Democrats, who have a differential harm of 0.149 versus White Democrats and a differential harm of 0.207 versus Black Republicans.

@@

To test the suitability of the model for representing the outcomes of hypothetical future elections, we use the model fitted to the primary elections to predict the outcome of the mayoral general election in November 2021.
Michelle Wu and Annissa Essaibi-George advanced to the general from the preliminary election.
We fix the model's loading matrix $\vb L$ to the the posterior mean of their estimated loadings.
We draw $s_{jk}$ from a $\Beta(20\bar s, 20(1-\bar s))$ distribution, where $\bar s$ is each candidate's share of the two-candidate vote from the preliminary election (59.7% Wu -- 40.3 Essaibi George).

>>>>

This intuition is confirmed by a closer analysis, summarized in Figure \ref{fig:al-maps}(f).
Across the state, the average harm is 0.082, which translates to around 161,000 voters.
Of these harmed voters, around 136,000 are Black, while 25,000 are White.
Similarly, 151,000 are Democratic, while only 10,000 are Republican.
Of course, the total number of each of these groups of voters is very different.
Normalizing by group sizes, the expected harm for a Black Democrat is 0.25, for a Black Republican is 0.015, for a White Democrat is 0.091, and for a White Republican is 0.0073.
Thus while the challenged plan differentially harms both Black voters and Democratic voters, it *especially* harms Black Democrats, who have a differential harm of 0.158 versus White Democrats and a differential harm of 0.235 versus Black Republicans.

@@

To test the suitability of the model for representing the outcomes of hypothetical future elections, we use the model fitted to the primary elections to predict the outcome of the mayoral general election in November 2021.
Michelle Wu and Annissa Essaibi-George advanced to the general from the preliminary election.
We fix the model's loading matrix $\vb L$ to the the posterior mean of their estimated loadings.
We draw $s_{jk}$ from a $\Beta(20\bar s, 20(1-\bar s))$ distribution, where $\bar s$ is each candidate's share of the two-candidate vote from the preliminary election (59.7% Wu -- 40.3% Essaibi George).
